\emeszida

### 2024-03-29 sigbovik/paper.tex
changed something

When the program is executed, it produces a single numeric output for each input pair. 
These outputs correspond remarkably closely to the values in the first column of Plimpton 322, as demonstrated in Figure~\ref{fig:graph}.
The correspondence is not perfect, however, and the values which should match lines 1, 5, and 6 of Plimpton 322 are significantly larger than expected.
This implies that, although the code on this tablet is clearly \textit{related} to Plimpton 322, it could not have been used to directly populate the table in that text.
Perhaps the outputs from this model were refined in some later step to produce the more exact ratios in the Plimpton text, or perhaps the Babylonians were disillusioned by the imprecision of their machine learning models and simply abandoned them for tried-and-true manual methods. 
Given how miniscule the cuneigramming corpus is relative to the larger body of Babylonian administrative writing, we lean towards the latter explanation.

%It is clear that the cuneogrammers were slowly developing their skills as some of the earlier and simpler methods date as far back as the Old Akkadian period (c. 2300--2150 BCE) while the perceptron tablet is from the Old Babylonian period (c. 1900--1600 BCE).

\begin{figure}\label{fig:graph}
    \includegraphics[width=0.5\textwidth]{graph.png}
    \caption{Outputs from the perceptron tablet vs.\ true value of each line from column 1 of Plimpton 322. If a points falls upon the line, the model output for that line exactly equals the value on Plimpton 322.}
    \label{fig:graph}
\end{figure}

The tablets preserve a number of methods for performing simple neural network calculations.
Simple array operations as well as the calculation of the dot product are included in the corpus.
All of this comes together in the large perceptron tablet.
It is clear that the cuneogrammers were slowly developing their skills as some of the earlier and simpler methods date as far back as the Old Akkadian period (c. 2300--2150 BCE) while the perceptron tablet is from the Old Babylonian period (c. 1900--1600 BCE).
Interestingly, the long weights at the end of the tablet very closely resemble the parameters of later astronomical calculations (see Figure \ref{fig:BM_34580}).

>>>>

When the program is executed, it produces a single numeric output for each input pair. 
These outputs correspond remarkably closely to the values in the first column of Plimpton 322, as demonstrated in Figure~\ref{fig:graph}.
The correspondence is not perfect, however, and the values which should match lines 1, 5, and 6 of Plimpton 322 are significantly larger than expected.
This implies that, although the code on this tablet is clearly \textit{related} to Plimpton 322, it could not have been used to directly populate the table in that text.
Perhaps the outputs from this model were refined in some later step to produce the more exact ratios in the Plimpton text, or perhaps the Babylonians were disillusioned by the imprecision of their machine learning models and simply abandoned them for tried-and-true manual methods. 
Given how miniscule the cuneogramming corpus is relative to the larger body of Babylonian administrative writing, we lean towards the latter explanation.

\begin{figure}
    \includegraphics[width=0.5\textwidth]{graph.png}
    \caption{Outputs from the perceptron tablet vs.\ true value of each line from column 1 of Plimpton 322. If a point falls upon the line, the model output for that line exactly equals the value on Plimpton 322.}
    \label{fig:graph}
\end{figure}

The tablets preserve a number of methods for performing simple neural network calculations.
Simple array operations as well as the calculation of the dot product are included in the corpus.
All of this comes together in the large perceptron tablet.
It is clear that the cuneogrammers were slowly developing their skills as some of the earlier and simpler methods date as far back as the Old Akkadian period (c. 2300--2150 BCE) while the perceptron tablet is from the Old Babylonian period (c. 1900--1600 BCE).
